TBD

### 2016-10-06 paper.tex
made section even better

The gradient based minimization algorithms that are generally used to solve least squares problems generally require the model $\bv$ to be differentiable
towards each model parameter. When the least squares problem is complex, which is the case for Eq.~\eqref{eq:red_least_squares}, it becomes less straightforward to apply these gradient based minimization methods. The reason being,
many complex functions are not analytic (no Taylor expansion around a fiducial point exists) and therefore not differentiable if we make use of classic differentiation. For instance if the 
classical definition of differentiation is used then $\frac{\partial z}{\partial \conj{z}}$, where $z \in \mathbb{C}$, does not exist.

@@

Recently Kreutz-Delgado and Sorber proposed an alternative strategy, which involves the use of Wirtinger calculus (Wirtinger 1927). The Wirtinger derivatives 
are defined to be 
\begin{align}
\frac{\partial}{\partial z} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} -  i \frac{\partial}{\partial y} \right ),&\frac{\partial}{\partial \conj{z}} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} +  i \frac{\partial}{\partial y} \right ). 
\end{align}

\cite{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that this framework can also be applied to redundant calibration. Analogous to Smirnov and Tasse, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the standard derivative to define the gradient operator then 
$\breve{\bv}$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole (cite smirnov). The fact that $\breve{\bv}$ is now analytic in its argument implies that we can use the complex Gauss-Newton
and Levenberg-Marquardt equivalent algorithms to so solve Eq.~\eqref{eq:red_least_squares_complex}.

>>>>

The gradient based minimization algorithms that are generally used to solve least squares problems generally require the model $\bv$ to be differentiable
towards each model parameter. When the least squares problem is complex, which is the case for Eq.~\eqref{eq:red_least_squares}, it becomes less straightforward to apply these gradient based minimization methods. The reason being,
many complex functions are not analytic (no Taylor expansion around a fiducial point exists) and therefore not differentiable if the classic notion of differentiation is used. For instance if the 
classical definition of differentiation is used then $\frac{\partial z}{\partial \conj{z}}$, where $z \in \mathbb{C}$, does not exist.

@@

Recently Kreutz-Delgado and Sorber proposed an alternative strategy, which involves the use of Wirtinger calculus (Wirtinger 1927). The Wirtinger derivatives 
are defined to be 
\begin{align}
\frac{\partial}{\partial z} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} -  i \frac{\partial}{\partial y} \right ),&\frac{\partial}{\partial \conj{z}} &= \frac{1}{2}\left ( \frac{\partial}{\partial x} +  i \frac{\partial}{\partial y} \right ). 
\end{align}
Using the above definitions we can now easily compute the following:
\begin{align}
\frac{\partial z}{\partial z} & = 1, & \frac{\partial \conj{z}}{\partial z}&=0, & \frac{\partial z}{\partial \conj{z}} & = 0, & \frac{\partial \conj{z}}{\partial \conj{z}}&=1.
\end{align}

\citet{Smirnov2015} recently proposed to use this Wirtinger framework instead of the classic real and imaginary approach to perform normal calibration. We will now show
that the Wirtinger framework can also be applied to redundant calibration. Analogous to \cite{Smirnov2015}, we recast Eq.~\eqref{eq:red_least_squares} to 
\begin{equation}
\label{eq:red_least_squares_complex}
\min_{\breve{\bz}} \|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$, $\breve{\bd} = [\bd,\conj{\bd}]^T$, $\breve{\bv} = [\bv,\conj{\bv}]$. Eq.~\eqref{eq:red_least_squares_complex} is the augmented counterpart of Eq.~\eqref{eq:red_least_squares}.
If we use the Wirtinger derivative instead of the classic notion of a derivative to define the gradient operator then 
$\bv$ becomes analytic in $\bz$ and $\conj{\bz}$ as a whole \citep{Smirnov2015}. The fact that $\breve{\bv}$ is now analytic in its argument has the immediate consequence that we can use the complex variants of the Gauss-Newton
and the Levenberg-Marquardt algorithm to solve Eq.~\eqref{eq:red_least_squares_complex}.
